Computer Science House Constitution

### 2019-03-31 articles.tex
Reference

% BEFORE CHANGES ARE MADE TO THIS DOCUMENT:
% -References will be automatically updated if any part is added, deleted, etc.
%  However, if a sub part is moved to a different part, its references must be
%  changed.
% -This document must be ratified by the House (as per the Constitution),
%  if changes are to be officialized.

@@

\asection{Active Membership}
\asubsection{Active Membership Qualifications}
Active Membership is open to all students currently enrolled at the Rochester Institute of Technology who have passed the Introductory Evaluation and their most recent Membership Evaluation.
\asubsection{Active Membership Selection}
Qualifying members may self-select into Active Membership by paying dues to the Financial Director and notifying the Evaluations Director.
\\*\\*
Any Alumni Member in bad standing (\ref{Alumni Membership Selection}) may become an Active Member by notifying the Evaluations Director of their intent to participate, who will bring them up for vote at the next Evaluations meeting.
If a majority is in favor of the return, the Alumni is reinstated as an Active Member with Off-Floor status effective immediately.
The decision will be announced at the following House meeting.
\asubsection{Active Membership Expectations}
Active members are expected to be active participants in the House as defined in \ref{Expectations of House Members}.
\asubsection{Active Membership Privileges}
Active Members receive the right to:
\begin{itemize}
	\item Vote on all issues brought before the House
	\item Reside on the House
	\item Hold an Executive Board office on the House
	\item Use Computer Science House facilities
	\item Attend Computer Science House functions
	\item Receive priority for available housing on the House when returning from cooperative education
	\item Guaranteed housing in compliance with the Residence Life policies regarding Special Interest Houses and the Housing Selection Process (if they have On-Floor status)
\end{itemize}
Active Members currently on co-op forfeit their right to vote on house issues, and likewise do not count towards quorum.
Exceptions may be made at the discretion of the Evaluations Director.
\asubsection{Active Membership Evaluations}
Active Members are evaluated semi-annually through the Evaluation Process as described in \ref{Evaluations Processes}.
Failure of the Evaluation Process could result in the member being asked to find alternative housing as soon as possible in accordance with all applicable Residence Life policies regarding room changes.
\asubsection{Active Membership Leave of Absence}
An Active member may at any time request a leave of absence using the process described in \ref{Leave of Absence}.
For the duration of an absence, a member:
\begin{itemize}
	\item Forfeits their right to vote
	\item Does not count towards quorum
	\item Will not be required to attend House Meeting
\end{itemize}
\asubsection{Active Membership Resignations}
An Active member may resign by submitting, in writing, the reason for resignation to the Chairman, or Evaluations Director.
Instead of forfeiting membership, Active members who resign may elect to become Alumni defined in \ref{Alumni Membership Selection}.
The resignation will take effect immediately and an announcement will be made at the following House Meeting.
\asubsection{Active Membership Term}
Active Membership shall last until the member: resigns or changes membership status.

@@

\asection{Resignations}
An Executive Board Member may resign their position by submitting in writing the reason for resignation to the House Chairman.
The resignation will be read at the following House Meeting and become effective at that time.
The office will become vacant and the selection process for a new member as described in section \ref{Appointment of an Interim Director} will begin at that time.

@@

\asection{Term}
\begin{enumerate}
\item The Election Process for the following year's Executive Board members shall begin in the middle of Spring semester.
\item The newly selected officers shall begin their terms on June 1 of that year and their terms shall end on May 31 of the following year.
\item The term of an officer will be abbreviated due to resignation, impeachment, or change in membership status.
\item Officers elected or selected during the course of the year due to an abbreviated term of the previous officer shall hold office until the end of the normal term.
\item When the task of an Ad Hoc Directorship has been completed, the directorship dissolves.
	When an Ad Hoc Director resigns, the directorship dissolves and must be reinstated with a new director.
\end{enumerate}

@@

% ARTICLE V - VOTING
\article{Voting}
This section outlines the different types of votes and ballots used to make House decisions and defines relevant terminology.
\asection{Definitions}
\asubsection{Total Number of Possible Votes}
The sum of the number of Active members eligible to vote (i.e. not on co-op)
\asubsection{Total Number of Votes Cast}
The Total Number of Votes Cast is defined as the total number of votes received for every voting option minus the number of abstentions.
\asubsection{Quorum}
A Quorum is defined by the minimum number of votes cast required for a vote to be official.
It is a fraction or a percentage of the total number of possible votes.
Any member present for an Immediate Vote or given a ballot who does not explicitly cast their vote is counted as an Abstention.
A Quorum is reached if the Total Number of Votes Cast plus the number of Abstentions is equal to or exceeding the minimum number of votes required.
\asubsection{Proxy Ballot}
A Proxy Vote is defined as any ballot that was cast by one member on behalf of another member.
Any member may cast a Proxy Vote for another member who is unable to actually participate in the vote.
A Proxy Vote must be explicitly written down and signed by the member not in attendance.
The count of all Proxy Vote must be recorded and announced in all votes.
Proxy Votes are only permissible where explicitly stated, at the discretion of the person chairing the vote.
\asubsection{Abstention}
An Abstention is defined as a vote indicating a neutral position in the vote.
A means to abstain must always be provided in a vote.
Abstentions are counted towards a Quorum, but not towards the Total Number of Votes Cast used to determine if a vote passes or not.
\asubsection{Vote Counters}
The chairperson of the vote is a vote counter and will additionally select two other members to count votes.

@@

\asubsubsection{Voting Period}
For constitutional modification, candidate selection, and officer removal votes, the voting period must be at least forty-eight (48) hours in length.
For any other type of vote, the voting period must be at least twenty-four (24) hours.
The minimum length of the voting period may be explicitly lengthened, but never shortened, in the text describing the actual vote.
\asubsection{Balloted Vote}
\asubsubsection{Method of Vote}
Votes are cast on paper ballots, which provide a means to indicate every possible option in the vote.
A ballot is then distributed to each House member eligible to cast a vote and collected in the designated ballot box for a pre-specified length of time.
At the end of the voting period, the person chairing the vote collects the ballots, closing the voting period.
The Vote Counters then tally the results.
\asubsubsection{Voting Period}
For constitutional modification, candidate selection, and officer removal votes, the voting period must be at least forty-eight (48) hours in length.
For any other type of vote, the voting period must be at least twenty-four (24) hours.
The minimum length of the voting period may be explicitly lengthened, but never shortened, in the text describing the actual vote.
\asubsection{Immediate Vote}
\asubsubsection{Method of Vote}
The person chairing the vote will state all possible ways to vote, then call out each possibility one at a time.
The chairing member will count the number of members casting their immediate vote for that possibility.
\asubsubsection{Voting Period}
An immediate vote lasts as long as it takes for all votes to be tallied.
\asubsection{Secret Immediate Vote}
\asubsubsection{Method of Vote}
The person chairing the vote will state all possible ways to vote, then call out each possibility one at a time.
Votes are kept anonymous.
The chairing member and Vote Counters will count the number of members casting their immediate vote for that possibility.
\asubsubsection{Voting Period}
A secret immediate vote lasts as long as it takes for all votes to be tallied.
\asubsection{Batch Vote}
When a Batch Vote is called for by the chair, a subset of the voting docket may be amended to a single vote.
A Two-Thirds Immediate Vote is required to allow a Batch Vote to take place.
If the call for Batch Vote passes, the subset may then be voted on, otherwise the docket remains unchanged.

@@

% ARTICLE VI - JUDICIAL
\article{Judicial}
The Executive Board may approve (by simple majority) a request (from a member) for a Judicial proceeding when an official clarification of the Constitution or By-Laws is required, there is a conflict among House Members, or a House interest needs resolution.
\asection{Formation of a Judicial Board}
A Judicial Board is made up of the Chairman, the Evaluations director, and an additional voting member of the Executive Board chosen by a majority vote among the Executive Board.
If either the Chairman or Evaluations Director are deemed biased or unfit for a position on the Judicial Board, they will be replaced by another voting member of the Executive Board by means of a simple majority vote amongst the remaining Executive Board members.
\asection{Judicial Investigation}
The Judicial Board will be responsible for making all necessary inquiries into the matter of the request brought to the Judicial Board.
\asection{Judicial Ruling}
The Judicial Board may present an official ruling following the Judicial Investigation.
This ruling may be appealed in the same manner as an Executive Board decision \ref{Appeals}.
\end{document}

>>>>

% BEFORE CHANGES ARE MADE TO THIS DOCUMENT:
% -References will be automatically updated if any part is added, deleted, etc.
%  However, if a sub part is moved to a different part, its references must be
%  changed.
% -This document must be ratified by the House (as per the Constitution),
%  then printed, signed, notarized, and placed in the House filing cabinet
%  if changes are to be officialized.

@@

\asection{Active Membership}
\asubsection{Active Membership Qualifications}
Active Membership is open to all students currently enrolled at the Rochester Institute of Technology who have passed the Introductory Evaluation and their most recent Membership Evaluation.
\asubsection{Active Membership Selection}
Qualifying members may self-select into Active Membership by paying dues to the Financial Director and notifying the Evaluations Director.
\\*\\*
Any Alumni Member in bad standing (\ref{Alumni Membership Selection}) may become an Active Member by notifying the Evaluations Director of their intent to participate, who will bring them up for vote at the next Evaluations meeting.
If a majority is in favor of the return, the Alumni is reinstated as an Active Member with Off-Floor status effective immediately.
The decision will be announced at the following House meeting.
\asubsection{Active Membership Expectations}
Active members are expected to be active participants in the House as defined in \ref{Expectations of House Members}.
\asubsection{Active Membership Privileges}
Active Members receive the right to:
\begin{itemize}
	\item Vote on all issues brought before the House
	\item Reside on the House
	\item Hold an Executive Board office on the House
	\item Use Computer Science House facilities
	\item Attend Computer Science House functions
	\item Receive priority for available housing on the House when returning from cooperative education
	\item Guaranteed housing in compliance with the Residence Life policies regarding Special Interest Houses and the Housing Selection Process (if they have On-Floor status)
\end{itemize}
Active Members currently on co-op forfeit their right to vote on house issues, and likewise do not count towards quorum.
Exceptions may be made at the discretion of the Evaluations Director.
\asubsection{Active Membership Evaluations}
Active Members are evaluated semi-annually through the Evaluation Process as described in \ref{Evaluations Processes}.
Failure of the Evaluation Process could result in the member being asked to find alternative housing as soon as possible in accordance with all applicable Residence Life policies regarding room changes.
\asubsection{Active Membership Leave of Absence}
An Active member may at any time request a leave of absence using the process described in \ref{Leave of Absence}.
For the duration of an absence, a member:
\begin{itemize}
	\item Forfeits their right to vote
	\item Does not count towards quorum
	\item Will not be required to attend House Meeting
\end{itemize}
\asubsection{Active Membership Resignations}
An Active member may resign by submitting, in writing, the reason for resignation to the Chairman, or Evaluations Director.
Instead of forfeiting membership, Active members who resign may elect to become Alumni defined in \ref{Alumni Membership Selection}.
The resignation will take effect immediately and an announcement will be made at the following House Meeting.
\asubsection{Active Membership Term}
Active Membership shall last until the member: resigns, fails the Evaluation Process, or changes membership status.

@@

\asection{Resignations}
An Executive Board Member may resign their position by submitting in writing the reason for resignation to the House Chairman.
The resignation will be read at the following House Meeting and become effective at that time.
The office will become vacant and the selection process for a new member as described in section \ref{Appointment of an Interim Director} will begin at that time. Following a resignation, an election must be held for the position vacated within two weeks from when the resignation took place. The Chairman may chair an immediate fifty percent vote \ref{\ref{Fifty Percent} to postpone the election by a specified time period with a spoken reason. The vote may not take place for elections for year end elections.

@@

\asection{Term}
\begin{enumerate}
\item The Election Process for the following year's Executive Board members shall begin in the middle of Spring semester.
\item The newly selected officers shall begin their terms on June 1 of that year and their terms shall end on May 31 of the following year.
\item The term of an officer will be abbreviated due to resignation, impeachment, failure of the evaluation process, or change in membership status.
\item Officers elected or selected during the course of the year due to an abbreviated term of the previous officer shall hold office until the end of the normal term.
\item When the task of an Ad Hoc Directorship has been completed, the directorship dissolves.
	When an Ad Hoc Director resigns, the directorship dissolves and must be reinstated with a new director.
\end{enumerate}

@@

% ARTICLE V - VOTING
\article{Voting}
This section outlines the different types of votes and ballots used to make House decisions and defines relevant terminology.
\asection{Definitions}
\asubsection{Total Number of Possible Votes}
The sum of the number of Active members eligible to vote (i.e. not on co-op)
\asubsection{Total Number of Votes Cast}
The Total Number of Votes Cast is defined as the total number of votes received for every voting option minus the number of abstentions.
\asubsection{Quorum}
A Quorum is defined by the minimum number of votes cast required for a vote to be official.
It is a fraction or a percentage of the total number of possible votes.
Any member present for an Immediate Vote or given a ballot who does not explicitly cast their vote is counted as an Abstention.
A Quorum is reached if the Total Number of Votes Cast plus the number of Abstentions is equal to or exceeding the minimum number of votes required.
\asubsection{Proxy Ballot}
A Proxy Vote is defined as any ballot that was cast by one member on behalf of another member.
Any member may cast a Proxy Vote for another member who is unable to actually participate in the vote.
A Proxy Vote must be explicitly written down and signed by the member not in attendance.
The count of all Proxy Vote must be recorded and announced in all votes.
Proxy Votes are only permissible where explicitly stated, at the discretion of the person chairing the vote.
\asubsection{Abstention}
An Abstention is defined as a vote indicating a neutral position in the vote.
A means to abstain must always be provided in a vote.
Abstentions are counted towards a Quorum, but not towards the Total Number of Votes Cast used to determine if a vote passes or not.
\asubsection{Vote Counters}
Vote Counters are the chairperson of the vote, and two randomly selected members.

@@

\asubsubsection{Voting Period}
For constitutional modification, candidate selection, and officer removal votes, the voting period must be at least forty-eight (48) hours in length.
For any other type of vote, the voting period must be at least twenty-four (24) hours.
The minimum length of the voting period may be explicitly lengthened, but never shortened, in the text describing the actual vote.
\asubsection{Balloted Vote}
\asubsubsection{Method of Vote}
Votes are cast on paper ballots, which provide a means to indicate every possible option in the vote.
A ballot is then distributed to each House member eligible to cast a vote and collected in the designated ballot box for a pre-specified length of time.
At the end of the voting period, the person chairing the vote collects the ballots, closing the voting period.
The Vote Counters then tally the results.
\asubsubsection{Voting Period}
For constitutional modification, candidate selection, and officer removal votes, the voting period must be at least forty-eight (48) hours in length.
For any other type of vote, the voting period must be at least twenty-four (24) hours.
The minimum length of the voting period may be explicitly lengthened, but never shortened, in the text describing the actual vote.
\asubsection}
\asubsubsection{Method of Vote}
The person chairing the vote will state all possible ways to vote, then call out each possibility one at a time.
The chairing member will count the number of members casting their immediate vote for that possibility.
\asubsubsection{Voting Period}
An immediate vote lasts as long as it takes for all votes to be tallied.
\asubsection{Secret Immediate Vote}
\asubsubsection{Method of Vote}
The person chairing the vote will state all possible ways to vote, then call out each possibility one at a time.
Votes are kept anonymous.
The chairing member and Vote Counters will count the number of members casting their immediate vote for that possibility.
\asubsubsection{Voting Period}
A secret immediate vote lasts as long as it takes for all votes to be tallied.
\asubsection{Batch Vote}
When a Batch Vote is called for by the chair, a subset of the voting docket may be amended to a single vote.
A Two-Thirds Immediate Vote is required to allow a Batch Vote to take place.
If the call for Batch Vote passes, the subset may then be voted on, otherwise the docket remains unchanged.

@@

% ARTICLE VI - JUDICIAL
\article{Judicial}
The Executive Board may approve (by simple majority) a request (from a member) for a Judicial proceeding when an official clarification of the Constitution or By-Laws is required, there is a conflict among House Members, or a House interest needs resolution.
\asection{Formation of a Judicial Board}
A Judicial Board is made up of the Chairman, the Evaluations director, and an additional voting member of the Executive Board chosen by a majority vote among the Executive Board.
If either the Chairman or Evaluations Director are deemed biased or unfit for a position on the Judicial Board, they will be replaced by another voting member of the Executive Board by means of a simple majority vote amongst the remaining Executive Board members.
\asection{Judicial Investigation}
The Judicial Board will be responsible for making all necessary inquiries into the matter of the request brought to the Judicial Board.
\asection{Judicial Ruling}
The Judicial Board may present an official ruling following the Judicial Investigation.
This ruling may be appealed in the same manner as an Executive Board decision \ref{Appeals}.

% ARTICLE VII - TEMPORARY AMENDMENTS
\article{Temporary Amendments}
In the case that an amendment should be temporary, the amendment's changes should be listed here. 
Each of these amendments is given a designated period of time, and will cease to exist immediately following the end of the period.
Occasionally, Temporary Amendments may become permanent through a referendum, which is described in detail as part of each Temporary Amendment. 
\asection{Changes to Evaluations}
During the 2018-2019 period the following will supercede the text otherwise found in this document.
\asubsection{Changes}
\asubsubsection{Change of Packet Percentage}
\ref{Creation of Accounts} currently stipulates that Introductory Members must acquire 60\% (rounded up to the nearest whole person) of required signatures (excluding those of Resident members who have not passed a Membership Evaluation) in the Introductory Packet or successfully complete Introductory Evaluations. 
During the described period, the percentage of required signatures in the Introductory Packet will be increased to 75\%. 
\asubsubsection{Changes to Packet Times}
Introductory Members will recieve \ref{The Introductory Packet} following the House Meeting or Evaluations Directorship meeting of the second week of each semester. 
Each Introductory Member will submit their packet at the end of week 3. 
\asubsubsection{Evaluation Period}
During the described period, the \ref{The Introductory Process} will begin during the first week of each semester.
The Executive Board may hold a Simple Majority vote to extend the Introductory Process or the Introductory Packet during the described period.
Additionally, \ref{Introductory Evaluation} occurs between the sixth and tenth week of each semester. 
\subsubsection{Referendum}
During the last house meeting of the second semester of the described period, a Two-Thirds vote is held, and if it passes, \ref{Changes to Evaluations} becomes permanent. 
\end{document}
